Comparison of dimensionality reduction schemes for parallel global optimization algorithms \thanks{The study was supported by the Russian Science Foundation, project No 16-11- 10150}

### 2018-05-16 2018/RSD/MultiEvolvents/RSD.tex
RSD: fixe typos

One of the possible ways to overcome the negative effects of using a numerical
approximation of evolvent (it destroys the information about the neighbour points in $\mathbb{R}^N$ space,
see \cite{Strongin1992}) consists in using the multiple mappings
\begin{equation}%\label{eq:142}
Y_L(x)=\left\{y^0(x),\ y^1(x),...,\ y^L(x)\right\}
\end{equation}
instead of single Peano curve $y(x)$ (see \cite{Strongin1992,strSergGO,Strongin1991}).

@@

%------------------------------------------------------------------------------
\section{Conclusions}
In the present work, 5 different Peano curve-type mappings applied to the dimensionality
reduction in the global optimization problems were considered.
From the preliminary comparison conducted in Sec.~\ref{sec:seq_comp}, one can make the
following conclusions:
\begin{itemize}
  \item the smooth evolvent and the non-univalent one demonstrate the best result in the
problems of small dimensionality and can be applied successfully in solving the problems with
the computational costly objective functions. The properties of these evolvents don't allow
developing the optimization algorithms scalable onto several cluster nodes based on these ones.
  \item the shifted evolvents introduce large overhead costs on the operation of the method due
to the requirement to adding an auxiliary functional constraint into the problem (\ref{eq:task}).
The experiments have demonstrated that up to 95\% of the search information account for the
points, in which the auxiliary constraint is computed only. The shifted evolvents can be used as
the base for the parallel algorithm from Sec.~\ref{sec:parallel_evolvents}. However, the costs of
processing the auxiliary points would result likely in a small speedup from the parallelization.
However, if the objective function is computation-costly enough, the use of these evolvents
could make sense.
  \item the rotated evolvents have provided an acceprable speed of convergence in the problems
of small dimensionality in the sequential mode. The use of these ones don't result in the
introduction of the auxiliary constraints that allows constructing an efficient parallel algorithm
based on these evolvents.
\end{itemize}

>>>>

One of the possible ways to overcome the negative effects of using a numerical
approximation of evolvent (it destroys the information about the neighbor points in $\mathbb{R}^N$ space,
see \cite{Strongin1992}) consists in using the multiple mappings
\begin{equation}%\label{eq:142}
Y_L(x)=\left\{y^0(x),\ y^1(x),...,\ y^L(x)\right\}
\end{equation}
instead of single Peano curve $y(x)$ (see \cite{Strongin1992,strSergGO,Strongin1991}).

@@

%------------------------------------------------------------------------------
\section{Conclusions}
In the present work, 5 different Peano curve-type mappings applied to the dimensionality
reduction in the global optimization problems were considered.
From the preliminary comparison conducted in Sec.~\ref{sec:seq_comp}, one can make the
following conclusions:
\begin{itemize}
  \item the smooth evolvent and the non-univalent one demonstrate the best result in the
problems of small dimensionality and can be applied successfully in solving the problems with
the computational costly objective functions. The properties of these evolvents don't allow
developing the optimization algorithms scalable onto several cluster nodes based on these ones.
  \item the shifted evolvents introduce large overhead costs on the operation of the method due
to the requirement to adding an auxiliary functional constraint into the problem (\ref{eq:task}).
The experiments have demonstrated that up to 95\% of the search information account for the
points, in which the auxiliary constraint is computed only. The shifted evolvents can be used as
the base for the parallel algorithm from Sec.~\ref{sec:parallel_evolvents}. However, the costs of
processing the auxiliary points would result likely in a small speedup from the parallelization.
However, if the objective function is computation-costly enough, the use of these evolvents
could make sense.
  \item the rotated evolvents have provided an acceptable speed of convergence in the problems
of small dimensionality in the sequential mode. The use of these ones don't result in the
introduction of the auxiliary constraints that allows constructing an efficient parallel algorithm
based on these evolvents.
\end{itemize}
